The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-10 paper/ms.tex
now has section on classical pulsators

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6,7}$
Timothy R. White,$^{5,8}$\newauthor
Daniel Huber,$^{9,10,11}$
Ashley Chontos,$^{9}$
Victor Silva Aguirre,$^{5}$
Victoria Antoci,$^{5}$\newauthor
Suzanne Aigrain,$^{3}$ 
Timothy R. Bedding,$^{10,5}$
Jie Yu,$^{10,5}$ 
Amalie Stokholm,$^{5}$\newauthor
Timothy van Reeth,$^{5,10}$
David W. Latham,$^{12}$,
Allyson Bieryla,$^{12}$
Gilbert A. Esquerdo,$^{12}$\newauthor
Paula Jofr\'{e},$^{13}$
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{9}$Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
$^{12}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{13}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile
}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C}. It has yielded the detection of gravity-mode period spacings in a red giant \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation of red giants \citep{rggmoderotation,2012A&A...548A..10M} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars as cool as the Sun and hotter \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence. \newpage

@@

\begin{figure}
\noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
\caption{\label{venn}
Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
\end{figure}
\newpage % hack because the venn diagram doesn't work

@@

\subsubsection{Classical Pulsators}
\label{pulsators}
The sample contains many $\delta\,\text{Sct}$ and $\gamma\,\text{Dor}$ variables, and several hybrid pulsators. \textcolor{red}{Simon - add text here.}
Including hotter stars, we also detect SPB pulsations in \textcolor{red}{some stars - Conny/Tim van Reeth?}.

@@

Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. The other example is the B3e star HD~183362 at $G = -2.576$. A detailed study of these stars will be presented by Antoci et al., in prep.

>>>>

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6,7}$
Timothy R. White,$^{5,8}$\newauthor
Timothy R. Bedding,$^{9,5}$
Allyson Bieryla,$^{10}$
David W. Latham,$^{10}$,
Conny Aerts,$^{11,12,13}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Dominic Bowman,$^{11,12,13}$
Ashley Chontos,$^{9}$\newauthor
Gilbert A. Esquerdo,$^{10}$
Daniel Huber,$^{14,15,9}$
Paula Jofr\'{e},$^{16}$
Simon Murphy,$^{5,9}$\newauthor
Timothy van Reeth,$^{5,9}$
Victor Silva Aguirre,$^{5}$
Amalie Stokholm,$^{5}$
Jie Yu,$^{9,5}$ \newauthor
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{9}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{10}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{11}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{12}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{13}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{14}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{15}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
$^{16}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C}. It has yielded the detection of gravity-mode period spacings in a red giant \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation of red giants \citep{rggmoderotation,2012A&A...548A..10M} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars as cool as the Sun and hotter \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.

@@

\begin{figure}
\noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
\caption{\label{venn}
Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
\end{figure}

@@

\subsubsection{Classical Pulsators}
\label{pulsators}

Amongst our sample are pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}. The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18}. These studies cover about 70 stars so far. However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties. One of the valuable outputs of our current work includes the reduced light curves of several early-B stars, which were only scarcely targeted in the nominal \kepler mission. The few that were monitored did not reveal suitable oscillation frequency patterns to achieve a unique mode identification, which is a requirement to perform asteroseismic modelling. The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution. The in-depth asteroseismic analysis of the smear data for the~B~stars in this work is beyond the scope of the current paper, as it requires additional ground-based follow-up spectroscopy. Such studies will be the subject of future work.

@@

Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main {}sequence. The other example is the B3e star HD~183362 at $G = -2.576$. A detailed study of these stars will be presented by Antoci et al., in prep.
